### 2017-04-14 Paper01_EnthalpyAndCrystallization.tex
Discussion - added some DSC notes, Results - added m value calcs.

\section{METHOD}
\glsresetall

@@

\section{RESULTS}
\glsresetall

@@

Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa system.
$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$

@@

>>>>

\section{METHOD}

@@

\section{RESULTS}

@@

Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa~ system. From the equations ... a fit of
$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$ was established. This give a $D^{*}=20.4$ which using $D^{*}=590/(m-16)$ Shuai2014 [4, 5] gives a fragility $m=44.9$.

@@

The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher. This higher heating rates were used because crystallization events for the films were different to differentiation at the lower heating rate. 
Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.
